Incentivizing Exploration by Heterogeneous Users

### 2018-06-06 algorithm_regret.tex
changes accepted

For the remainder of the proof, we consider phases $s$
with $\EarlyCut{s} \leq \TieCutoff$.
We first consider agents \AgV incurring positive regret less than \EarlyCut{s}.
Let $A_s$ be the set of types satisfying 
$\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{\Second{\AgV}}) \leq \EarlyCut{s}$.
By Assumption~\ref{A1}, and because $\EarlyCut{s} \leq \TieCutoff$,
the total measure of $A_s$
is $\AlmostTied{\EarlyCut{s}} \leq \TieDensity \cdot \EarlyCut{s}$.
Then, by Lemma~\ref{lem:phase-length},
the expected number of pulls in phase $s$ by agents in $A_s$  
is bounded above by $\TieDensity \EarlyCut{s} \cdot \ARMNUM \log(s)$.
\dkdelete{and the total expected number of pulls by these agents by
$\sum_{s=1}^T \TieDensity \EarlyCut[2]{s} \ARMNUM \log(s)$.
Consider}
Any agent \AgV incurring positive regret less than $\EarlyCut{s}$
must have a type in $A_s$,
\dkdelete{Moreover, this agent's regret is bounded above by $\EarlyCut{s}$.}
so the expected total regret from such agents,
\dkedit{summed over all phases,} is at most
\begin{equation}
\sum_{s=1}^{T} \TieDensity \EarlyCut[2]{s} \cdot \ARMNUM \log(s).
\label{equ:small_regret_bound}
\end{equation}

>>>>

For the remainder of the proof, we consider phases $s$
with $\EarlyCut{s} \leq \TieCutoff$.
We first consider agents \AgV incurring positive regret less than \EarlyCut{s}.
Let $A_s$ be the set of types satisfying 
$\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{\Second{\AgV}}) \leq \EarlyCut{s}$.
By Assumption~\ref{A1}, and because $\EarlyCut{s} \leq \TieCutoff$,
the total measure of $A_s$
is $\AlmostTied{\EarlyCut{s}} \leq \TieDensity \cdot \EarlyCut{s}$.
Then, by Lemma~\ref{lem:phase-length},
the expected number of pulls in phase $s$ by agents in $A_s$  
is bounded above by $\TieDensity \EarlyCut{s} \cdot \ARMNUM \log(s)$.
Any agent \AgV incurring positive regret less than $\EarlyCut{s}$
must have a type in $A_s$,
so the expected total regret from such agents,
summed over all phases, is at most
\begin{equation}
\sum_{s=1}^{T} \TieDensity \EarlyCut[2]{s} \cdot \ARMNUM \log(s).
\label{equ:small_regret_bound}
\end{equation}
